Implementation of poloidal density variation in collision operator

### 2017-12-05 doc/PoloidalVariationInCollisionOperator_code.tex
updated documentation

Rather than creating many if-statements in the current implementation of the collision operator, for sake of clarity we separate the two implementations with one if-statement directly before the various contributions to the collision operator are calculated. If \texttt{poloidalVariationInCollisionOperator = .false.} the first block is executed, which contains the original code.

\begin{lstlisting}
if (.not. poloidalVariationInCollisionOperator) then   !! Added by AI (2017-09).
\end{lstlisting}

\noindent Otherwise, if \texttt{poloidalVariationInCollisionOperator = .true.}, \texttt{includePhi1 = .true.} and \texttt{includePhi1InKineticEquation = .true.} we proceed to the new block where poloidal density variation is included.

\begin{lstlisting}
else if (includePhi1 .and. includePhi1InKineticEquation) then! Do with poloidal density variation
\end{lstlisting}

@@

% Some notes:
Basically the structure is the following: the densoty might not always be corresponding to the row index (since we might have cross terms) but the distribution function is ALWAYS the column index, which is SpeciesB, that is why we use  f1b in the end

>>>>

Rather than creating many if-statements in the current implementation of the collision operator, for sake of clarity we separate the two implementations with one if-statement directly before the various contributions to the collision operator are calculated. If \texttt{Phi1} is included and \texttt{poloidalVariationInCollisionOperator = .true.} the contribution from the collision operator is calculated taking poloidal density variation into account.

\begin{lstlisting}
 if (poloidalVariationInCollisionOperator .and. includePhi1 .and. includePhi1InKineticEquation) then
\end{lstlisting}

Otherwise the second block is executed, which contains the original code.

@@
